ODGI: scalable tools for pangenome graphs

### 2021-05-31 manuscript/main.tex
topic 3rd

    \topic{odgi stats, bin, depth \& degree} users can retrieve metrics describing the graph properties, such as the number of
    nodes, edges, paths, and graph length. \odgi\ also offers more advanced tools for interrogating the graphs.
    \cmd{odgi bin} summarizes the path information into bins of specified size, enabling a summarized view of
    gigabase scale graphs. \cmd{odgi depth} returns the node depth as defined by query criteria, allowing users to
    detect the complex regions in the graph due to sequences with highly identical repeats. Complex motifs can be also
    detected with \cmd{odgi degree}, which returns the node degree as defined by query criteria. High degree nodes
    are the mirror of misassemblies or problems in the pangenome building, making the tool useful for debugging the
    process as well.

>>>>

    \topic{odgi stats, bin, depth \& degree} pangenome statistics allow exploring genome complexity at different
    levels of abstraction. \cmd{odgi stats} returns the number of nodes, edges, paths, and graph length, while
    \cmd{odgi bin} summarizes the path information into bins of specified size, enabling a summarized view of
    gigabase scale graphs. \cmd{odgi depth} and \cmd{odgi degree} return the node depth and degree, respectively, as
    defined by query criteria, allowing users to detect complex regions due to sequences with highly identical
    repeats, or problems in the pangenome graph.
